### 2020-11-12 thesis/chap_1.tex
final fix to bibliography

%[we are building on past work]
This work is the continuation of recent research efforts on the connectivity of the region: \cite{albert_applying_2017} and \citep{rayfield_priorisation_2018}. In a seminal paper, \cite{albert_applying_2017} laid out some of the methodological steps we follow such as umbrella species selection and habitat suitability analysis. They also included a simple land use change model that was parameterized to replicate plausible change in the region. \cite{meurant_selecting_2018} developed the criteria for reducing the number of focal species from fourteen to five. They showed that because species had redundant connectivity needs, modelling the needs for 5 species resulted in qualitatively similar results than when modelling the needs of all 14 species, such as in \cite{albert_applying_2017}. While Rayfield et al. (\citeyear{rayfield_priorisation_2018}) extended the spatial scale of the analysis to include the Saint Lawrence lowlands ecoregion, they demonstrated that we could exploit this redundancy to reduce the computing time needed for the connectivity analysis. This is an important development because land use change simulations are also computationally intensive.

@@

For the allocation step, we use an advanced cellular automata (CA) modelling tool (markov-chain based) called ST-Sim, a package of the free software SyncroSim. ST-Sim allows for more complex simulation than a classic CA as it allows for complex neighbouring rules with state and age cell tracking. It is also built to handle large datasets and can be scripted to run in parallel. It is important to note that although it is the first time RF is used with ST-Sim (to our knowledge), this hybrid modelling approach (coined “RF-CA”) has been used successfully in other land use change modelling projects \citep{kamusoko_simulating_2015, gounaridis_random_2019}. ST-Sim can be customized to function under multiple different types of inputs. The two main inputs are transition probability and transition targets. Readers should refer to Daniel el al. (\citeyear{daniel_state-and-transition_2016}) for a more in-depth overview of how ST-Sim and SyncroSim functions. \\

@@

The species selection process is unchanged from \cite{rayfield_priorisation_2018}. The species are the Northern short-tailed Shrew (\textit{Blarina brevicauda}), the American marten (\textit{Martes americana}), the Red-Backed Salamander (\textit{Plethodon cinereus}), the Wood Frog (\textit{Rana sylvatica}), and the Black Bear (\textit{Ursus americanus}). As previusly mentionned, these  species are considered umbrella species from the standpoint of ecological connectivity in the region, as it has been shown that modeling the connectivity needs of those 5 species was equivalent to modeling the needs of 14 species in the study region \citep{meurant_selecting_2018, albert_applying_2017}. We now give a short description of these 5 species, adapted from \cite{albert_applying_2017}.

@@

Habitat suitability analysis consists in reclassifying land use data into a resistance surface which is then used to model connectivity. For each of the maps obtained from the land use change analysis (for each of the timestep in every iteration and for each of the 5 species), we followed the following steps to reclass land use into resistance:
\begin{enumerate}
\item Classify the landscape as \textbf{forest} and \textbf{non forest}.
\item Reclassify non-forest pixels into resistance following the supplementary tables in \cite{rayfield_priorisation_2018}, with only a few alterations. See table \ref{tab:key_non_forest} for the reclassification key.
\item Clump the forest landscape into contiguous \textbf{patches} using queen case neighborhood (includes diagonal).
\item Reclassify pixels in all patches as suitable (value = 1) unsuitable (value = 0) or moderately suitable (value = 0.5), based on forest age and type, and following guidelines in the supplementary tables in  \citeauthor{rayfield_priorisation_2018}.  The key for such reclassification is recorded in table \ref{tab:suit_pixls}.
\item  Compute the mean patch value based on the clumped outputs.
\item Classify each patch as \textbf{possibly suitable} or \textbf{unsuitable}, with a cut-off value of 0.5.
\item Among the suitable patches, calculate their size.
\item Classify \textbf{possibly suitable} patches into \textbf{fully suitable} patches or \textbf{too small} patches based on their size, using the values provided by \citeauthor{rayfield_priorisation_2018} (see table \ref{tab:patch_size}).
\item Reclassify patches into resistance, once again following the guidelines in \citeauthor{rayfield_priorisation_2018}'s supplementary tables. See table \ref{tab:hab_or_not} for the reclassification key.
\item Patch the re-classified non-forest map with the re-classified patches map. 
\end{enumerate}

>>>>

%[we are building on past work]
This work is the continuation of recent research efforts on the connectivity of the region \citep{albert_applying_2017, rayfield_priorisation_2018}. In a seminal paper, \cite{albert_applying_2017} laid out some of the methodological steps we follow such as umbrella species selection and habitat suitability analysis. They also included a simple land use change model that was parameterized to replicate plausible change in the region. \cite{meurant_selecting_2018} developed the criteria for reducing the number of focal species from fourteen to five. They showed that because species had redundant connectivity needs, modelling the needs for 5 species resulted in qualitatively similar results than when modelling the needs of all 14 species, such as in \cite{albert_applying_2017}. While \cite{rayfield_priorisation_2018} extended the spatial scale of the analysis to include the Saint Lawrence lowlands ecoregion, they demonstrated that we could exploit this redundancy to reduce the computing time needed for the connectivity analysis. This is an important development because land use change simulations are also computationally intensive.

@@

For the allocation step, we use an advanced cellular automata (CA) modelling tool (markov-chain based) called ST-Sim, a package of the free software SyncroSim. ST-Sim allows for more complex simulation than a classic CA as it allows for complex neighbouring rules with state and age cell tracking. It is also built to handle large datasets and can be scripted to run in parallel. It is important to note that although it is the first time RF is used with ST-Sim (to our knowledge), this hybrid modelling approach (coined “RF-CA”) has been used successfully in other land use change modelling projects \citep{kamusoko_simulating_2015, gounaridis_random_2019}. ST-Sim can be customized to function under multiple different types of inputs. The two main inputs are transition probability and transition targets. Readers should refer to \cite{daniel_state-and-transition_2016} for a more in-depth overview of how ST-Sim and SyncroSim functions. \\

@@

The species selection process is unchanged from \cite{rayfield_priorisation_2018}. The species are the Northern short-tailed Shrew (\textit{Blarina brevicauda}), the American marten (\textit{Martes americana}), the Red-Backed Salamander (\textit{Plethodon cinereus}), the Wood Frog (\textit{Rana sylvatica}), and the Black Bear (\textit{Ursus americanus}). As previusly mentionned, these  species are considered umbrella species from the standpoint of ecological connectivity in the region, as it has been shown that modeling the connectivity needs of those 5 species was equivalent to modeling the needs of 14 species in the study region \citep{meurant_selecting_2018}. We now give a short description of these 5 species, adapted from \cite{albert_applying_2017}.

@@

Habitat suitability analysis consists in reclassifying land use data into a resistance surface which is then used to model connectivity. For each of the maps obtained from the land use change analysis (for each of the timestep in every iteration and for each of the 5 species), we followed the following steps to reclass land use into resistance:
\begin{enumerate}
\item Classify the landscape as \textbf{forest} and \textbf{non forest}.
\item Reclassify non-forest pixels into resistance following the supplementary tables in \cite{rayfield_priorisation_2018}, with only a few alterations. See table \ref{tab:key_non_forest} for the reclassification key.
\item Clump the forest landscape into contiguous \textbf{patches} using queen case neighborhood (includes diagonal).
\item Reclassify pixels in all patches as suitable (value = 1) unsuitable (value = 0) or moderately suitable (value = 0.5), based on forest age and type, and following guidelines in the supplementary tables in  \cite{rayfield_priorisation_2018}.  The key for such reclassification is recorded in table \ref{tab:suit_pixls}.
\item  Compute the mean patch value based on the clumped outputs.
\item Classify each patch as \textbf{possibly suitable} or \textbf{unsuitable}, with a cut-off value of 0.5.
\item Among the suitable patches, calculate their size.
\item Classify \textbf{possibly suitable} patches into \textbf{fully suitable} patches or \textbf{too small} patches based on their size, using the values provided by \cite{rayfield_priorisation_2018} (see table \ref{tab:patch_size}).
\item Reclassify patches into resistance, once again following the guidelines in \cite{rayfield_priorisation_2018}'s supplementary tables. See table \ref{tab:hab_or_not} for the reclassification key.
\item Patch the re-classified non-forest map with the re-classified patches map. 
\end{enumerate}

### 2020-11-12 thesis/thesis.tex
re
final fix to bibliography

% Bib style
%\setcitestyle{authoryear,open={((},close={))}}
  \usepackage[
    style=apa,
    maxbibnames=20,
    maxcitenames=2,
    minbibnames=19,
    mincitenames=1,
    isbn = false,
    backend=biber,
    uniquelist = false,
    natbib=true %, 
    %refsection=chapter
  ]{biblatex}

>>>>

% Bib style
\usepackage[
  style=authoryear,
  giveninits=true,
  maxcitenames=2,
  mincitenames=1,
  maxbibnames=21,
  minbibnames=19,
  isbn = false,
  backend=biber,
  uniquelist = false,
  natbib=true
]{biblatex}
